Guarded Recursion in Agda via Sized Types

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
Sacchini

We focus on two of these techniques in which productivity is encoded
at the level of types: sized types and guarded recursion. A sized type
 is a type annotated with the number of unfoldings that
elements of this type can undergo \cite{Hughes96}. Sized types have been implemented
in Agda and can be used in
combination with coinductive records to specify
coinductive types \cite{Copatterns,AVW-normalization}, as exemplified
by Abel and Chapman's work \cite{AC14}.
There also are other approaches to sized types, one of those is developed by Sacchini
\cite{Sacchini13}, but the latter allows less terms to be typed
compared to Agda's approach.

>>>>

We focus on two of these techniques in which productivity is encoded
at the level of types: sized types and guarded recursion. A sized type
 is a type annotated with the number of unfoldings that
elements of this type can undergo \cite{Hughes96}. Sized types have been implemented
in Agda and can be used in
combination with coinductive records to specify
coinductive types \cite{Copatterns,AVW-normalization}, as exemplified
by Abel and Chapman's work \cite{AC14}.
There also are other approaches to sized types.
One of those is developed by Sacchini \cite{Sacchini13}, which allows less terms to be typed
compared to Agda's approach.
